responseToFrankeTypicalUse...

### 2015-12-15 models/midScalarInvestigation.Rmd
updated output - language tweaks

---
title: "responeToFrankeTypicalUse"
author: "Ben Peloquin"
date: "December 14, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 3
---
```{r}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)
```

>>>>

---
title: "responseToFrankeTypicalUse..."
author: "Ben Peloquin"
date: "December 14, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 3
---
```{r}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)
```
